---
output:
  word_document: default
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



## Quantum and Oscillator Strategy and other Strategies 
## Summary and Implement


## `r format(Sys.time(), "%Y-%m-%d")`



# Moving Average Convergence/Divergence
Here I used yahoo_Finance as my data source.
When a user want to use this program, he can just change the date.
Here, I use XOM for example.
Load data:
```{r}
library("quantmod") 
#reset the date and ticker
start <-as.Date("2017-12-11")
end <-as.Date("2018-12-07")
ticker <- "XOM"
#
getSymbols(ticker,src = "yahoo", from = start,to = end)
head(XOM)
```

Reset the parameter of MACD.
In my example, the fast EMA is 12, slow EMA is 26, signal line is 9.
```{r}
#reset the parameter
macd <- MACD(XOM[, "XOM.Close"], 12, 26, 9, maType = "EMA") 
# draw the graph
plot(macd[, 1], type = "l", col = "blue")
lines(macd[, 2], type = "l", col = "red")
#legend(201, 1.5, c("MACD", "Singal_line"), lty = c(1,1), col = c("blue", "red"), bty = "n")
```


Begin to build the strategy.
Here, I use some trick to spot the cross point, where the trader should implement his trading.
```{r}
n <- sum(is.na(macd[,2]))
Cp <- c()
Cp <- rep(0, n)
for(i in (n+1) : nrow(macd)){
  if(macd[i, 1] > macd[i, 2]){
    Cp[i] <- 1} 
  else{
      Cp[i] <- -1}
}
# xomsignal is the trasaction signal
xomsignal <- rep(0,nrow(macd))
for(i in (n+1) : nrow(macd)){
  if((Cp[i] - Cp[i - 1]) == 2) {
    xomsignal[i] <- 'buy'}
  else if((Cp[i] - Cp[i - 1]) == -2){
    xomsignal[i] <- 'sell'}
}
XOM2<- cbind(as.data.frame(XOM), xomsignal)
signals <- subset(XOM2,xomsignal!=0)
signals
```

Set a the initial capital and transaction fee.
For example:
initial capital = 10000
transaction fee = 5 (including sell and buy)


```{r}
# set the initial capital and transaction fee
cap<-10000
fee <- 5
# calculate the odd or even
transaction.times <- nrow(signals) %/% 2 * 2
if(nrow(signals)%%2 == 0){
  parity <- "even"
}else if(nrow(signals)%%2 == 1){
  parity <- "odd"
}
# calculate the number of shares 
shares<-rep(0,transaction.times)
for(i in 1:(transaction.times/2)) {
  shares[2*i-1]=cap/(signals$XOM.Close[2*i-1])
  }
shares<-floor(shares)
# calculate the profits 
if (parity == "odd"){
  PL<-cbind(signals[-nrow(signals),],shares)
}else{
  PL<-cbind(signals,shares)
}

profit<-rep(0,transaction.times)
for(i in 1:(transaction.times/2)){
  if(PL$xomsignal[1] == "buy"){
  profit[2*i] <- PL$shares[2*i-1]*(PL$XOM.Close[2*i]-PL$XOM.Close[2*i-1])-fee }
  if(PL$xomsignal[1] == "sell"){
  profit[2*i] <- PL$shares[2*i-1]*(PL$XOM.Close[2*i]-PL$XOM.Close[2*i-1])-fee }
  }
final<-cbind(PL,profit)
final[,5:9]
```

Use the data to calculate return rate, sharpe ratio and so on.
For example:
risk-free rate is 0.511.
```{r}
# set risk-free rate
rf <- 0.511
#
mean(final$profit) 
var(final$profit) 
sd(final$profit) 
rf<-5.11/100
ri<-rep(0,transaction.times) 
for(i in 1:(transaction.times/2)){
  ri[2*i]<-log(final$XOM.Close[2*i]/final$XOM.Close[2*i-1]) }
ri<-ri[ri!=0]
sharpe<-(mean(ri)-rf)/sd(ri-rf) 
sharpe
```

# RSI- Relative Strength Index
We still use the data of XOM.
1.set the time period, N =14
2.set overbought and oversold market parameter, up = 80, down=20

```{r}
# set parameter
N <- 14
up <- 80
down <- 20
# EMA
rsi<-RSI(XOM$XOM.Close,N,maType = EMA)
ts.plot(rsi,ylim=c(0,100),main="RSI time series under EMA",ylab="RSI") 
overbought<-c(rep(up,length(rsi)))
oversold<-c(rep(down,length(rsi)))
lines(overbought,col="red")
lines(oversold,col="blue")
```

Simulate the trading process. The trick to find the point is similar to MACD.
```{r}
state1<-c(rep(0,length(rsi)))
n <- sum(is.na(rsi))
for(i in (n+1):length(rsi)){
  if(rsi[i] < 20){state1[i]<-1}
  if(rsi[i] > 80){state1[i]<--1}
} 
trade1<-c(rep(0,length(rsi))) 
for(i in 15:length(rsi)){
  if(((state1[i]-state1[i-1])==1)&(state1[i-1]==0)) {
    trade1[i]<-'buy'}
  if(((state1[i]-state1[i-1])==-1)&(state1[i-1]==0)){
    trade1[i]<-'sell' }
  }
trade_set1<-cbind(as.data.frame(XOM),trade1) 
trade_signal1<-subset(trade_set1,trade1!=0)
trade_signal1
```

SMA is similar.
```{r}
rsi<-RSI(XOM$XOM.Close,N,maType = SMA)
ts.plot(rsi,ylim=c(0,100),main="RSI time series under SMA",ylab="RSI") 
overbought<-c(rep(up,length(rsi)))
oversold<-c(rep(down,length(rsi)))
lines(overbought,col="red")
lines(oversold,col="blue")

state1<-c(rep(0,length(rsi)))
n <- sum(is.na(rsi))
for(i in (n+1):length(rsi)){
  if(rsi[i] < 20){state1[i]<-1}
  if(rsi[i] > 80){state1[i]<--1}
} 
trade1<-c(rep(0,length(rsi))) 
for(i in 15:length(rsi)){
  if(((state1[i]-state1[i-1])==1)&(state1[i-1]==0)) {
    trade1[i]<-'buy'}
  if(((state1[i]-state1[i-1])==-1)&(state1[i-1]==0)){
    trade1[i]<-'sell' }
  }
trade_set1<-cbind(as.data.frame(XOM),trade1) 
trade_signal1<-subset(trade_set1,trade1!=0)
trade_signal1

```

# Pair trading strategy
Here we use XOM and CVS to implement pair trading strategy.
ticker1 = XOM
ticker2 = CVS 
```{r}
library(tseries)
if(FALSE){
# set the tickers and time period.
 start <- as.Date("2015-11-30")
 end <- as.Date("2017-11-30")
 ticker1 = "XOM"
ticker2 = "CVS"
getSymbols(ticker1,src = "yahoo", from = start,to = end)
getSymbols(ticker2,src = "yahoo", from = start,to = end)
# get the graphs
close1 <- as.matrix(XOM$XOM.Close)
close2 <- as.matrix(CVS$CVS.Close)
logr1 <- diff(log(close1))
logr2 <- diff(log(close2))
}

setwd("/Users/yifuhe/Desktop")
CVS <-read.csv("CVX.csv") 
XOM <-read.csv("XOM.csv") 
x <-diff(log(XOM$Close))
y <-diff(log(CVS$Close))
fit2<-lm(y~x)
summary(fit2)
z<-c(NA)
```

build the strategy
```{r}
# Estimate the co-integrating relation
if(FALSE){
plot(x,y,main = "scatter plot of the log returns")
fit <- lm(logr2~logr1)
summary(fit)
intercept <- coef(fit)[1]
slope <- coef(fit)[2]
abline(fit,cex = 1.3,pch = 16, col = "red" )
res<-fit$residuals
plot(fit,which=1)
# adf test
adf.test(res)
}


#png(file = "linearregression of XOM and CVX.png")
plot(x,y,col = "blue",main = "scatter plot",xlab="XOM",ylab="CVX")
abline(fit2,cex = 1.3,pch = 16,col = "red")

z <- fit2$residuals
stdz<-sd(z)
delta <-2*stdz
plot(z,ylab="residential",xlab="time",main="Plot of Residentials")
abline(h=-delta,col="blue")
abline(h=delta,col="red")
# adf test
adf.test(z)
```
if P-value is less than 0.01, we can rejected the null Hypothesis.
For example: 
use delta = 2 * std(z_t)
accuracy = 0.001
Portfolio: long --- logr2
          short --- logr1
```{r}
if(FALSE){
# set delta
delta<-2*sd(res)
accuracy = 0.001
##
date<-as.Date(row.names(as.data.frame(XOM))[-1])
error <- logr2-slope*logr1 - intercept
data <- data.frame(date,logr1,logr2,error)
data$signal=c(rep("none",nrow(data)))
data[abs((data$error+delta))<=accuracy,]$signal<-"buy"
data[abs((data$error-delta))<=accuracy,]$signal<-"sell"
data$order <- seq(nrow(data))
trade_signal <- subset(data, data$signal != "none")
trade_signal}
##


slope <- coef(fit2)[2]
intercept <- coef(fit2)[1]
date<-as.Date(XOM$Date[-1])
yt_axt<-y-slope*x
data<-data.frame(date,x,y,yt_axt)
data$signal = rep("none",nrow(data))
data[abs((data$yt_axt+delta-intercept))<=0.001,]$signal<-"buy" 
data[abs((data$yt_axt-delta-intercept))<=0.001,]$signal<-"sell"
data$order = seq(nrow(data))
trade<-subset(data,data$signal!="none")
trade
```

Calculate P/L
Suppose that the transaction size is 1 contract.
```{r}
if(FALSE){
close1 <- XOM$Close[(trade_signal$order)+1]
close2 <- CVS$Close[(trade_signal$order)+1]
signal <- trade_signal$signal
signal[signal == "sell"] = 1
signal[signal == "buy"] = -1
signal <- as.numeric(signal)
signal1 <- signal*slope
signal1[length(signal1)] = -2*slope
signal2 <- signal*(-1)
signal2[length(signal2)] = 2
pnl1 <- signal1 %*% close1
pnl2 <- signal2 %*% close2
pnl <- pnl1 +pnl2
pnl}

# need to figure out why get different outcome when use same data from different source
close1 <- XOM$Close[(trade$order)+1]
close2 <- CVS$Close[(trade$order)+1]
signal <- trade$signal
signal[signal == "sell"] = 1
signal[signal == "buy"] = -1
signal <- as.numeric(signal)
signal1 <- signal*slope
signal1[length(signal1)] = -2*slope
signal2 <- signal*(-1)
signal2[length(signal2)] = 2
pnl1 <- signal1 %*% close1
pnl2 <- signal2 %*% close2
pnl <- pnl1 +pnl2
pnl
```



